Project-II by Group Sydney

### 2015-12-20 Projet II/report/paper.tex
Add RFs

The normal support vector machine is a technique used for binary classification. The goal is to divide the space using an hyperplan in a way to maximize the margin, which represents the distance between closest members of the two classes. It is an interesting method because it has a regularization parameter which help to avoid overfitting. Another advantages is we can easily change the kernel function in order to try to find better boundaries. However, what is difficult is to find good parameters. We might have many support vectors and overfit if we set the $C$ too large and on the contrary if it is small, we might have not enough support vector and underfit. However, the best results we can obtain with support vector machine need to have a small imbalanced between the positive and negative examples. As seen in the section "Data visualization and analysis", there classes are not very well balanced as much for the binary classification as the multi-class classification. We have use the same algorithm we have seen in the lab $SMO$.

@@

\subsection{Decision Trees}

@@

>>>>

The normal support vector machine is a technique used for binary classification. The goal is to divide the space using an hyperplan in a way to maximize the margin, which represents the distance between closest members of the two classes. It is an interesting method because it has a regularization parameter which help to avoid overfitting. Another advantages is we can easily change the kernel function in order to try to find better boundaries. However, what is difficult is to find good parameters ($C$, $\gamma$). $\gamma$ is the kernel scale parameter which is related to how the data are scattered. We might have many support vectors and overfit if we set the $C$ too large and on the contrary if it is small, we might have not enough support vector and underfit. However, the best results we can obtain with support vector machine need to have a small imbalanced between the positive and negative examples. As seen in the section "Data visualization and analysis", there classes are not very well balanced as much for the binary classification as the multi-class classification. We have use the same algorithm we have seen in the lab $SMO$.

We have used the method \textit{fitcecoc} in matlab. We have used k-fold cross valiation to find $C$ and $\gamma$ and have set the margin $C=1$, and $\gamma = 1$. Only the linear kernel function was available in this mode, and so, gaussian kernel might give better results.

@@

\subsection{Bootstrap Aggregation}

As we have seen in the lecture, decision trees are good because the training and the prediction is quite fast, even with many features or large dataset but have a high variance. The idea of decision trees, is to have a several questions where to answer yes/no and to move in the tree. At the end, the leaves give the corresponding class. To construct this list of questions, we divide recursively the space in a way to minimize the cost of impurity (depending of the threshold to find and the current feature). The depth of the tree is a parameter.

The idea of bootstrap aggregation is to average several decision trees. It will help to reduce the variance and avoid overfitting. It generates $m$ new training sets of the same size, by sampling uniformly and with replacement the original training set. Then we have $m$ decision trees which will grows independently with their own generated training sets. Finally, to predict the class it takes the average over all the trees. In order to find those parameters $m$ and the maximum depth of the tree, we have also used k-fold cross validation and the best values are $m = 200$ and maximum depth of $512$ for the binary classification and for the multi-class case $m = 500$ and maximum depth also of $512$.

@@

In order to evaluate our different models, we have split our data in two sets of $80\%$ and $20\%$ for the training and the test sets. We choose this percentage in order to have still enough data for the training set and also enough to estimate correctly our models on the testing set. We learn only on the training set and then use the test set in order to estimate the error using the \textit{Balanced Error Rate}. This error compute the average percentage of misclassification per class. It allows us to avoid the case of the $90\%/10\%$ and having a good error. We have also used k-fold cross validation to tune the parameters up of our different models. We set $k=10$ because we have a lot of data, splitting them into $10$ folds seems reasonable ($4320$ data samples for the training set and $480$ for the testing set). We repeated the experiment $10$ times with different seeds in order to split the data in a unique random way for each trial and so try to have an unbiased estimation error. We couldn't increase the number of experiments because some methods are really slow.
